---
title: "Data import from HCA"
output: html_document
vignette: >
  %\VignetteIndexEntry{Data import from HCA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8} 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following codes import data of loom file(s) to analyze with workflow `Rcollectlworkflow` to table "file".

## Install packages
```{r, message=FALSE, warning=FALSE}
BiocManager::install("hca")
BiocManager::install("Bioconductor/AnVIL")
BiocManager::install("LoomExperiment")
BiocManager::install("yubocheng/Rcollectlworkflow")
```

## Get manifests

Variable filters (HCA filter object) need to be provided to identify loom file(s) for analysis, then manifests of the file(s) can be retrieved.

```{r, message=FALSE}
library(hca)
library(AnVIL)
library(dplyr)
library(Rcollectlworkflow)

filters <- filters(
  projectTitle = list(is = "Census of Immune Cells"),
  organPart = list(is = "bone marrow"),
  fileFormat = list(is = "loom"),
  isIntermediate = list(is = FALSE))

manifest_tibble <- get_manifest_tibble(filters)
manifest_tibble
```

## Import manifest file date to table "file"

Three variables: manifest_tibble, sample, mem_gb are needed to import file data to table "file". Sample should be one of column names from manifest_tibble, for example: donor_organism.biomaterial_core.biomaterial_id, cell_suspension.biomaterial_core.biomaterial_id, etc. Default value for mem_gb is 60 GB.

```{r, eval=FALSE}
sample = "donor_organism.biomaterial_core.biomaterial_id"
update_file_avtable(manifest_tibble, sample)
avtable("file")
```

## Run workflow

To run `Rcollectlworkflow`, click Rcollectlworkflow under WORKFLOWS tab, select file as "Step 1 Select root entity type:". For INPUTS, select attribute this.file_id for variable fileId, attribute this.knitr_eval for variable knitr_eval, attribute this.sample for variable sample, and attribute this.mem_gb for variable mem_gb. For OUTPUTS, attributes could be filled in by "Use defaults". After saving the workflow, it could be run by selecting the loom file to analyze for "Step 2 SELECT DATA".

## Pull workflow output

Workflow outputs could be pulled and viewed with `R`.

```{r, message=FALSE, eval=FALSE}
avworkspace("bioconductor-rpci-yubo/Rcollectlworkflow")
avworkflow_jobs()
fls <- avworkflow_files()
fls
gsutil_cp(fls |> filter(file == "cell_type_classification.rds") |> pull("path"), ".")
dir()
readRDS("cell_type_classification.rds")
```

## `R` session information

```{r session_info, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 120)
session_info()
```
