---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  out.width = "100%",
  echo = TRUE, 
  eval = FALSE
)
```

```{r,echo=FALSE,eval=FALSE}
## Generate the ./README.md (relative to base folder)
rmarkdown::render(input = "inst/scripts/README.Rmd", output_dir = ".")
```

# Rcollectl Workflow

The vignette in this package follows single-cell analysis Workflow (workflow chapters of the “Orchestrating Single-Cell Analysis with Bioconductor” book) to analyze loom file from HCA dataset and tracks computing resources usage with R package `Rcollectl`.

Suggested computing resources: 60 GB memory, 16 CPUs when parameter knitr_eval set to TRUE to knit the vignette.

Build docker image with files in inst/docker:
```{bash,echo=FALSE,eval=FALSE}
docker build -t bioconductor_docker_workflow_hca_loom:devel .
```

Knit vignette with built docker image and generate output at LOCAL_DIRECTORY:
```{bash,echo=FALSE,eval=FALSE}
docker run -it -v LOCAL_DIRECTORY:/output --rm \
	--env knitr_eval=FALSE \
	--env fileId="1c0434e8-df9d-54f9-9534-74ae512b10de" \
	--env sample="cell_suspension.biomaterial_core.biomaterial_id" \
	bioconductor_docker_workflow_hca_loom:devel 
```
